Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-09-03 doc/main_jfm.tex
wrapped up Sec 4 again

Figure~\ref{figure9} shows the simulation of two JP vesicles in a
shear flow with shear rate $\chi=0.005$. Using the pre-relaxed $58$-body
JP vesicle in previous sections, we duplicate the state to have the
initial configuration shown in panel (a). The two centers of mass are at
$(-10,0)$ and $(10,0)$. In all panels, the blue and red curves show the
trajectory of the two JP vesicle centroids. They have nearly
completed a full period by $t=4000$ as shown in panel (h). We also
observe an adhesive effect between the two JP vesicles that is set up
by the hydrophobic interactions and repulsive force. Similar dynamics
have been observed between a pair of adhering vesicles in a shear flow
(\cite{qua-vee-you2019, abb-far-ezz-ben-mis2021}). This adhesive
behavior is absent when two JP vesicles are well-separated.

The fluid pressure profiles snapshots are given in
Figure~\ref{figure10}. Since the initial JP vesicles are pre-relaxed,
there is initially no pressure jump between the internal and external
fluids (panel (a)). Panels (b)--(d) show the configurations when $t =
\{500,1000,1500\}$ and the streamlines are plotted in the background for
all panels. We include the numerical results using a continuum model in
all insets and these comparisons give a qualitative agreement between
two models.

@@

With a similar setup in the case of two JP vesicles in a shear flow,
we use the same two pre-relaxed $58$-body JP vesicles and consider
their dynamics in an extensional flow with extensional rate
$\chi=0.005$. This extensional flow is stretching in the $y$ direction
and squeezing in the $x$ direction. Figure~\ref{figure11} shows how the
initial placement of the JP vesicles affects the dynamics. When two
centroids are both placed symmetrically on the $x$-axis (case (i)), the
JP vesicles reach a steady equilibrium. If one centroid is placed
above the $x$-axis (case (ii)), the two JP vesicle move together and
then upward. The migration of the right JP vesicle is a consequence
of the adhesive effect created by the hydrophobic interactions. When the
two centroids start on opposite sides of the $x$-axis (case (iii)), they
eventually diverge from one another along the $y$-axis. Finally, when
the two centroids start on opposite sides of the $x$-axis, but with a
greater displacement (case (iv)), the JP vesicles move much faster
toward $\pm y$-directions.

Figure~\ref{figure12} shows numerical results when the centroids of two
bodies are placed at $(-10,-0.1)$ and $(10,0.1)$ (case (iii) from
Figure~\ref{figure11}). With this setup, the two
JP vesicles eventually separate along $y$-direction and we compare
the results against a continuum model as shown in all insets.  Panels
(b)--(d) show the transient behavior of the JP vesicles and continuum
vesicles transitions under an extensional flow. In both the
coarse-grained model and the continuum model, the vesicles initially
converge towards one other and then diverge along the $y$-axis. The
behavior of the streamlines in both cases are similar. The pressure is
initially largest in the gap formed by two JP vesicles and decreases
during the separation. The short range repulsion plays an important role
to avoid structure collisions.
%and this result can be
%compared with some findings in continuum modeling simulations.

@@

%\todo[inline]{Make figure of the paths of the two centroids....}

>>>>

Figure~\ref{figure9} shows the simulation of two JP vesicles suspended
in a shear flow with shear rate $\chi=0.005$. We duplicate the
pre-relaxed $58$-body JP vesicle from previous sections to construct the
initial configuration shown in Figure~\ref{figure9}(a). The two centers
of mass are at $(-10,0)$ and $(10,0)$. In all panels, the blue and red
curves show the trajectory of the two JP vesicle centroids. They have
nearly completed a full period by $t=4000$. We also observe an adhesive
effect between the two JP vesicles that is set up by the hydrophobic
interactions and repulsive force. Similar dynamics have been observed
between a pair of adhering vesicles in a shear flow
(\cite{qua-vee-you2019, abb-far-ezz-ben-mis2021}). This adhesive
behavior is absent when two JP vesicles are well-separated.

Snapshots of the fluid pressure are in Figure~\ref{figure10}. Since the
initial JP vesicles are pre-relaxed, there is initially no pressure jump
between the internal and external fluids (panel (a)). Panels (b)--(d)
show the configurations when $t = \{500,1000,1500\}$, and the
streamlines are plotted in the background for all panels. We include the
numerical results from a continuum model in all insets and these
comparisons give a qualitative agreement between two models.

@@

Using a similar setup to the shear case, we suspend the same two
pre-relaxed $58$-body JP vesicles and consider their dynamics in an
extensional flow with extensional rate $\chi=0.005$. This extensional
flow is stretching in the $y$ direction and squeezing in the $x$
direction. Figure~\ref{figure11} shows how the initial placement of the
JP vesicles affects the dynamics. When two centroids are both placed
symmetrically on the $x$-axis (case (i)), the JP vesicles reach a steady
equilibrium. If one centroid is placed above the $x$-axis (case (ii)),
the two JP vesicle move together and then upward. The migration of the
right JP vesicle is a consequence of the adhesive effect caused by the
hydrophobic interactions. When the two centroids start on opposite sides
of the $x$-axis (case (iii)), they eventually diverge from one another
along the $\pm y$-directions. Finally, when the two centroids start on
opposite sides of the $x$-axis, but with a greater displacement (case
(iv)), the JP vesicles move much faster along the $\pm y$-directions.

Figure~\ref{figure12} shows numerical results when the centroids of the
two Janus particles are placed at $(-10,-0.1)$ and $(10,0.1)$ (case
(iii) from Figure~\ref{figure11}). With this setup, the two JP vesicles
eventually separate along the $\pm y$-directions and we compare the
results against a continuum model as shown in all insets. Panels
(b)--(d) show the transient behavior of the JP vesicles and the
continuum vesicles under an extensional flow. In both the coarse-grained
model and the continuum model, the vesicles initially converge towards
one other and then diverge along the $y$-axis. The behavior of the
streamlines in both cases are similar. The pressure is initially largest
in the gap formed by two JP vesicles and decreases during the
separation. The short range repulsion plays an important role to avoid
structure collisions.
%and this result can be
%compared with some findings in continuum modeling simulations.

@@
